Whole genome alignment with wavefront inception

### 2022-04-24 manuscript/main.tex
remove bioinformatics references
nsf ppos funding

\subtitle{Genome Analysis}

@@

\history{Received on XXXXX; revised on XXXXX; accepted on XXXXX}

\editor{Associate Editor: XXXXXXX}

@@

We gratefully acknowledge support from NIH/NIDA U01DA047638 (EG) and efforts by Dr. Nicole Soranzo to establish a pangenome research unit at the Human Technopole in Milan, Italy (AG).
\linebreak
\linebreak
\textit{Conflict of Interest}: none declared.

>>>>

\subtitle{ } %Genome Analysis}

@@

\history{ } %Received on XXXXX; revised on XXXXX; accepted on XXXXX}

\editor{ } %Associate Editor: XXXXXXX}

@@

We gratefully acknowledge support from NIH/NIDA U01DA047638 and NSF PPoSS Award \#2118709 (EG) and efforts by Dr. Nicole Soranzo to establish a pangenome research unit at the Human Technopole in Milan, Italy (AG).
\linebreak
\linebreak
\textit{Conflict of Interest}: none declared.
